News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-09-04 rupnik2015.tex
figure updated

\begin{figure}[tbp]
\centering
\includegraphics[width=10cm]{lsi.pdf}
\caption{\label{fig:lsi} LSI multilingual corpus matrix decomposition.}
\todo{Missing matrix S of singular values!!!}
\end{figure}

@@

\textbf{Hub language characteristic}
In the case of Wikipedia we observed that even though the training resources are scarce for certain language pairs, there often exists indirect training data that we can use as a proxy -- hub language.\todo{Check this, I prettified it.}

>>>>

\begin{figure}[tbp]
\centering
\includegraphics[width=10cm]{lsi.pdf}
\caption{\label{fig:lsi} LSI multilingual corpus matrix decomposition.}
\end{figure}

@@

\textbf{Hub language characteristic}
In the case of Wikipedia, we observed that even though the training resources are scarce for certain language pairs, there often exists indirect training data. By considering a third language, which has training data with both languages in the pair,  we can use the composition of learned maps as a proxy. We refer to this third language as a hub language.
